### 2019-05-22 2-Chapters/5-Chapter/chapter5.tex
So long

\paragraph{Interpretation of the hypothesis of knowning $M$ for real-world networks.}
%
One could criticize our approach if we study a wireless networks with no central coordination from the gateway,
in particular where the devices cannot be assigned to a channel or be assigned a unique ID by the gateway when they first log in the network.
Then in such networks, if one wants to apply an algorithm like \MCTopM-\klUCB,
the $M$ devices need to known their number $M$, and have to receive it from the gateway, as it is the only part of this example of network which knowns $M$.
It seems unrealistic to ask the gateway to send the fixed value $M$ to each device, and not a unique ID to each device, for instance $\mathrm{id}^j\in[K]$.

@@

\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \Selfish-\klUCB{} & $250 \pm 34$ & $735 \pm 85$ & $3010 \pm 472$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        \RhoRand-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$1422 \pm 1051$} & \textcolor{red}{$9030 \pm 1922$} & \textcolor{red}{$7264 \pm 1009 $} \\
        \hline
        \RandTopM-\klUCB{} & $268 \pm 45$ & $941 \pm 217$ & $437 \pm 367$ \\
        \RandTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$688 \pm 614$} & \textcolor{red}{$4256 \pm 2701$} & \textcolor{red}{$1155 \pm 544$} \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        \MCTopM-\klUCB{} + \textcolor{red}{Estimate $M$} & \textcolor{red}{$563 \pm 546$} & \textcolor{red}{$1560 \pm 1293$} & \textcolor{red}{$618 \pm 29$} \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly.}
    \label{table:5:meanRegretSimulationsEstimatingM}
% \end{footnotesize}
\end{table}

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar increase on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large (on the three algorithms and two cases, about $\times 3.4$), and consistent on the different algorithm.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\cO(1)$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected, and much worse than \MCTopM.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of \MCTopM-\klUCB.

@@

\begin{table}[ht]
    % \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized Multiple play \klUCB{} & $\mathbf{91 \pm 21}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0 \pm 0}$ \\
        \Selfish-\klUCB{} & $249 \pm 35$ & $728 \pm 94$ & $2953 \pm 501$ \\
        \hline
        \textsc{Sic-MMAB} & $1705 \pm 340$ & $3915 \pm 300$ & $1713 \pm 52$ \\
        Improved \MusicalChair{} & $\textcolor{red}{12149 \pm 60}$ & $\textcolor{red}{22341 \pm 77}$ & $\textcolor{red}{27462 \pm 85}$ \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, for the ``no sensing'' case.}
    \label{table:5:meanRegretSimulationsNoSensing}
% \end{footnotesize}
\end{table}

@@

In all the models of IoT networks considered in this thesis, we assume that \emph{the different IoT devices cannot communicate with each other}, and can only communicate with a unique gateway.
Of course, this hypothesis can be removed, and in practice in some families of wireless networks, communication between devices are possible.
Note that this extension is not considering a graph of distributed agents all playing cooperatively to solve a unique bandit game, like it is studied in the ``graph bandit'' problem.
What we are interested here is an extension of the model where players can send some bits to one or all the other players, at every time steps or some time steps.

@@

In this extension, performance is still evaluated by a system regret, now defined as the difference between the sum of the cumulated rewards by the $M$ players, and the utility of any matching.
The question is to know if it is possible to obtain a logarithmic --or even sub-linear-- regret in this problem is more difficult that for the model presented in Section~\ref{sec:5:model}.
This question was first answered in \cite{Bistritz18}, and proposed an algorithm based on alternating three phases, and increasing their lengths after the end of each epoch ($2^p$ for the $p$-th epoch).
First, players explore in order to estimate the expectations of the arm rewards ; then players use their ``Game of Thrones'' dynamics (inspired by Musical Chair \cite{Rosenski16}) and play the optimal solution most of the time ; finally players play the action they played most of the time in the recent GoT phases.
% combining Musical Chair with an epoch-based alternative phases of forced exploration and pure exploitation.
They analyse their ``Game of Thrones'' algorithm and proved that it achieves a regret of $\cO((\log(T))^{2+\kappa})$ for any positive constant $\kappa$, as small as possible, if $\kappa$ is known by the algorithm.

@@

% DONE run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        \hline
        \rhoLearn-\klUCB{} + \klUCB{} & $546 \pm 190$ & $1172 \pm 295$ & $1416 \pm 347$ \\
        \rhoLearn-\klUCB{} + Bayes-UCB & $561 \pm 219$ & $1204 \pm 394$ & $1363 \pm 331$ \\
        \rhoLearn-\klUCB{} + Exp3 & $529 \pm 175$ & $1659 \pm 331$ & $5134 \pm 976$ \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        \hline
    \end{tabular}
    \caption{Comparing \RhoRand{} and \rhoLearn on a simple MP bandit problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}

@@

On the first hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in[M]$ knows its ID $j$ (see above the discussion we give on this unrealistic assumption).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our algorithm \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches the conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in[M]$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.

@@

\TODOL{Explain that we think the following approach can work very efficiently:

    - Combine \MCTopM{} with \GLRklUCB{} instead of \klUCB,
    - and incorporate also the detected change-points by B-\GLR{} test in the orthogonalization procedure: after any change-point, the player is not sitting anymore.
    - Modification: only a change-point on the arm on which player is sitting can make him move? It's already the case: the \GLR{} test can only detect change-point on an arm that was played, and the \MCTopM{} orthogonalization procedure forces to play the same arm as long as the player is sitting.
}

@@

% ----------------------------------------------------------------------------
\subsection{A note on SMPyBandits}

We have implemented in SMPyBandits \cite{SMPyBandits} the following extensions: evaluating $M$ on the fly (Section~\ref{sub:5:unknownNumberOfPlayers}), piece-wise stationary multi-player bandits (Section~\ref{sub:5:towardsNonStationaryModels}).
We have not yet implemented the other extensions, but we are interested to do it, and it is one of the major future work left on our library.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/X}}, for tickets number \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}.

>>>>

\paragraph{Interpretation of the hypothesis of knowning $M$ for real-world networks.}
\label{par:5:knowingYourIDinMPBanditsGame}
%
One could criticize our approach if we study a wireless networks with no central coordination from the gateway,
in particular where the devices cannot be assigned to a channel or be assigned a unique ID by the gateway when they first log in the network.
Then in such networks, if one wants to apply an algorithm like \MCTopM-\klUCB,
the $M$ devices need to known their number $M$, and have to receive it from the gateway, as it is the only part of this example of network which knowns $M$.
It seems unrealistic to ask the gateway to send the fixed value $M$ to each device, and not a unique ID to each device, for instance $\mathrm{id}^j\in[K]$.

@@

\begin{table}[ht]
\begin{small}  % WARNING
    \centering
    \begin{tabular}{cc|ccc}
    \textbf{Algorithms} & \textbf{Hyp. on $M$} & $M=3$ players & $M=6$ players & $M=9$ players \\
        \hline
        Centralized multiple-play
        & Known $M$ & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \Selfish
        & Don't need $M$ & $250 \pm 34$ & $735 \pm 85$ & $3010 \pm 472$ \\
        \hline
        \multirow{2}{*}{\RhoRand}
        & Known $M$ & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        & \textcolor{red}{Estimate $M$} & \textcolor{red}{$1422 \pm 1051$} & \textcolor{red}{$9030 \pm 1922$} & \textcolor{red}{$7264 \pm 1009 $} \\
        \hline
        \multirow{2}{*}{\RandTopM}
        & Known $M$ & $268 \pm 45$ & $941 \pm 217$ & $437 \pm 367$ \\
        & \textcolor{red}{Estimate $M$} & \textcolor{red}{$688 \pm 614$} & \textcolor{red}{$4256 \pm 2701$} & \textcolor{red}{$1155 \pm 544$} \\
        \hline
        \multirow{2}{*}{\MCTopM}
        & Known $M$ & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        & \textcolor{red}{Estimate $M$} & \textcolor{red}{$563 \pm 546$} & \textcolor{red}{$1560 \pm 1293$} & \textcolor{red}{$618 \pm 29$} \\
        \hline
    \end{tabular}
    \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, comparing algorithms which knows $M$ against algorithms which estimate $M$ on the fly. All use \klUCB.}
    \label{table:5:meanRegretSimulationsEstimatingM}
\end{small}  % WARNING
\end{table}

One can observe in Table~\ref{table:5:meanRegretSimulationsEstimatingM} the empirical performances of different algorithms in an example problem, in each case of low, medium and maximum number of players ($M=3,6,9$ for $K=9$ arms).
The three algorithms \RhoRand, \RandTopM{} and \MCTopM{} all suffer from similar increase on their regret when they have to estimate $M$ on the fly (written ``Estimate $M$'' in red, in Table~\ref{table:5:meanRegretSimulationsEstimatingM}). Our proposals are still much more efficient than \RhoRand{} when using the procedure to estimate $M$ described from \cite{Anandkumar11}.
For the two non-extreme cases ($M=3,6$), the performance drop when having to estimate $M$ is quite large,
% (on the three algorithms and two cases, about $\times 3.4$),
and consistent on the different algorithms.
The extreme case of $M=K$ players is of highest interest, as \MCTopM{} achieves a very small regret (proved to be $\cO(1)$ as it is just the expected time of the orthogonalization process), while the same algorithm with unknown $M$ suffers from a much larger regret.
In this extreme case, \RhoRand{} and its extension both perform very closely, as expected, and much worse than \MCTopM.
%
Additional simulations, for increasing time horizons $T$, confirmed the expected order-optimal regret of this extension of \MCTopM-\klUCB.

@@

\begin{table}[ht]
    % \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithms} $\;$ \textbackslash $\;$ \textbf{Number of players} & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized Multiple play \klUCB{} & $\mathbf{91 \pm 21}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0 \pm 0}$ \\
        \Selfish-\klUCB{} & $249 \pm 35$ & $728 \pm 94$ & $2953 \pm 501$ \\
        \hline
        \textsc{Sic-MMAB} & $1705 \pm 340$ & $3915 \pm 300$ & $1713 \pm 52$ \\
        Improved \MusicalChair{} & $\textcolor{red}{12149 \pm 60}$ & $\textcolor{red}{22341 \pm 77}$ & $\textcolor{red}{27462 \pm 85}$ \\
        \hline
    \end{tabular}
    % \caption{Mean regret $\pm$ $1$ std-dev, for different algorithms on the same problem with $M=3,6,9$, for the ``no sensing'' case.}
    \caption{Comparison for different algorithms on the same problem with $M=3,6,9$ players, for the ``no sensing'' case. We give the mean regret $\pm$ $1$ std-dev, and more work is needed on our implementation on Improved \MusicalChair. The results on \textsc{Sic-MMAB} appear to confirm the numerical experiments in the paper \cite{BoursierPerchet18}.}
    \label{table:5:meanRegretSimulationsNoSensing}
% \end{footnotesize}
\end{table}

@@

In all the models of IoT networks considered in this thesis, we assume that \emph{the different IoT devices cannot communicate with each other}, and can only communicate with a unique gateway.
Of course, this hypothesis can be removed, and in practice in some families of wireless networks, communication between devices are possible.
Note that this extension is not considering a graph of distributed agents all playing cooperatively to solve a unique bandit game, like it is studied in the ``\emph{graph bandit}'' problem.
What we are interested here is an extension of the model where players can send some bits to one or all the other players, at every time steps or some time steps.

@@

In this extension, performance is still evaluated by a system regret, now defined as the difference between the sum of the cumulated rewards by the $M$ players, and the utility of any matching.
The question is to know if it is possible to obtain a logarithmic --or even sub-linear-- regret in this problem is more difficult that for the model presented in Section~\ref{sec:5:model}.
This question was first answered in \cite{Bistritz18}, and proposed an algorithm based on alternating three phases, and increasing their lengths after the end of each epoch ($2^p$ for the $p$-th epoch).
First, players explore in order to estimate the expectations of the arm rewards ; then players use their ``Game of Thrones'' dynamics (inspired by Musical Chair \cite{Rosenski16}) and play the optimal solution most of the time ; finally players play the action they played most of the time in the recent GoT phases.
% combining Musical Chair with an epoch-based alternative phases of forced exploration and pure exploitation.
They analyze their ``Game of Thrones'' algorithm and proved that it achieves a regret of $\cO((\log(T))^{2+\kappa})$ for any positive constant $\kappa$, as small as possible, if $\kappa$ is known by the algorithm.

@@

% DONE run the simulations with N=100 and not N=4
% for M in 3 6 9; do DEBUG=False SAVEALL=False NOPLOTS=True M=$M K=9 N_JOBS=-1 N=100 T=10000 make moremultiplayers; read; done
\begin{table}[ht]
% \begin{footnotesize}
    \centering
    \begin{tabular}{c|ccc}
    \textbf{Algorithm} $\;$ \textbackslash $\;$ Number of players & $M=3$ & $M=6$ & $M=9$ \\
        \hline
        Centralized multiple-play \klUCB{} & $\mathbf{92 \pm 20}$ & $\mathbf{70 \pm 16}$ & $\mathbf{0}$ \\
        \hline
        \RhoRand-\klUCB{} & $417 \pm 103$ & $2481 \pm 449$ & $6639 \pm 1035$ \\
        \hline
        \rhoLearn-\klUCB{} + \klUCB{} & $546 \pm 190$ & $1172 \pm 295$ & $1416 \pm 347$ \\
        \rhoLearn-\klUCB{} + Bayes-UCB & $561 \pm 219$ & $1204 \pm 394$ & $1363 \pm 331$ \\
        \rhoLearn-\klUCB{} + Exp3 & $529 \pm 175$ & $1659 \pm 331$ & $5134 \pm 976$ \\
        \hline
        \MCTopM-\klUCB{} & $244 \pm 39$ & $401 \pm 55$ & $44 \pm 13$ \\
        \hline
    \end{tabular}
    \caption{Comparing \RhoRand{} and \rhoLearn{} on a simple MP bandit problem with $K=9$ arms.}
    \label{table:5:comparisonRhoRandRhoLearn}
% \end{footnotesize}
\end{table}

@@

On the first hand, piece-wise stationary multi-players MAB can be tackled by extending algorithms developed for the single-player case.
In \cite{WeiSrivastava18Distributed}, the authors study exactly the same multi-players bandit model as our model, and they propose two distributed algorithms that can efficiently be used by $M \leq K$ players to achieve sub-linear regret for piece-wise stationary problems, essentially by considering it as a harder case of a stationary problem. \\
\indent
The proposed the RR-SW-UCB\# algorithm, which combines their SW-UCB\# algorithm, previously proposed in \cite{WeiSrivastava18Abruptly}, and a Round-Robin hoping, under the assumption that each user $j\in[M]$ knows its ID $j$ (we criticize this unrealistic assumption in Section~\ref{par:5:knowingYourIDinMPBanditsGame} above).
The SW-UCB\# algorithm is discussed more in details in the literature review of Chapter~\ref{chapter:6} below.
%
If $\Upsilon_T$ is bounded by $\Upsilon_T = \bigO{T^{\gamma}}$, for a known $\gamma$ but an unknown $\Upsilon_T$, they prove for instance in Theorem~2 \cite{WeiSrivastava18Distributed} that the expected cumulative regret of their RR-SW-UCB\# algorithm is bounded by $R_T = \bigO{T^{\frac{1+\gamma}{2}} \log(T)}$ (what we call the centralized system regret).
This bound is of the same order as the bound obtained by the same authors for the SW-UCB\# algorithm in \cite{WeiSrivastava18Abruptly} for the single-player case.
If $\Upsilon_T = \bigO{T^{\gamma}}$, this bound is comparable to the results obtained for most of the research literature on piece-wise stationary bandits (earlier works like D-UCB in \cite{Garivier11UCBDiscount} have the $\log(T)$ outside the square root, while more recent works all improved this aspect and have the $\log(T)$ in the square root, like for instance our algorithm \GLRklUCB{} in \cite{Besson2019GLRT} and presented in Chapter~\ref{chapter:6}).
Even if their analysis is not explicit regarding the constant, in the case where $\Upsilon_T = \bigO{T^{\gamma}}$ for a known $\gamma$, their regret upper-bound actually matches the conjectured lower-bound, up to a logarithmic factor $\log(T)$. \\
%
\indent
And finally, even though numerical simulations in their papers \cite{WeiSrivastava18Abruptly,WeiSrivastava18Distributed} are interesting and confirm the regret upper-bounds, they do not compare with any other algorithm, and it is left as an interesting future work to study this direction in more details.
Sadly, a major drawback of their work is that assume that player $j\in[M]$ knows its index $j$, and as we explained above this small hypothesis is actually quite strong, as it allows players to be already orthogonal, and it reduces greatly the difficulty of the decentralized bandit problem.

@@

% \TODOL{Explain that we think the following approach can work very efficiently:

%     - Combine \MCTopM{} with \GLRklUCB{} instead of \klUCB,
%     - and incorporate also the detected change-points by B-\GLR{} test in the orthogonalization procedure: after any change-point, the player is not sitting anymore.
%     - Modification: only a change-point on the arm on which player is sitting can make him move? It's already the case: the \GLR{} test can only detect change-point on an arm that was played, and the \MCTopM{} orthogonalization procedure forces to play the same arm as long as the player is sitting.
% }

@@

% ----------------------------------------------------------------------------
\subsection{Some future work on SMPyBandits}

We have implemented in SMPyBandits \cite{SMPyBandits} the following extensions: evaluating $M$ on the fly (Section~\ref{sub:5:unknownNumberOfPlayers}), piece-wise stationary multi-player bandits (Section~\ref{sub:5:towardsNonStationaryModels}).
We have not yet implemented the other extensions, but we are interested to do it, and it is one of the major future work left on our library.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/}}, for tickets number \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}.

### 2019-05-22 2-Chapters/Conclusion/conclusion.tex
So long

    \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyse from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still very interesting model.
We present different variants of the multi-player MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
\end{itemize}

@@

>>>>

    \item
The second half of this thesis, Part~\ref{part:MABIOT}, presents our main contributions.
% Chapter 4
In Chapter~\ref{chapter:4}, we first propose some models for realistic IoT wireless networks, in discrete times and with no central coordination between end-devices.
% In two different models, with or without retransmissions, we showed that end-devices can learn independently to increase their successful transmission rates in the network, by using low-cost MAB algorithm. We also present a proof-of-concept that implements such network on real radio hardware and validates our model and proposed algorithms.
% Chapter 5
Because the models studied for realistic IoT networks were found to be intractable to analyze from a theoretical point of view, mainly due to the large number of algorithms interacting at random times in a noisy environment,
in Chapter~\ref{chapter:5}, we study a weaker but still very interesting model.
We present different variants of the multi-player MAB model, and we propose the state-of-the-art algorithm for the variant with collision information (\MCTopM-\klUCB).
% Chapter 6
Finally, in Chapter~\ref{chapter:6}, we remove the stationary hypothesis on the single-player MAB problem, and we analyze a new actively adaptive algorithm (\GLRklUCB).
%
For the last two chapters, our proposed algorithms attain state-of-the-art performances both on numerical simulations and on the regret bounds obtained in our theoretical analyses.
\end{itemize}

@@

\TODOL{Explain that we think the following approach can work very efficiently:

    - Combine \MCTopM{} with \GLRklUCB{} instead of \klUCB,
    - and incorporate also the detected change-points by B-\GLR{} test in the orthogonalization procedure: after any change-point, the player is not sitting anymore.
    - Modification: only a change-point on the arm on which player is sitting can make him move? It's already the case: the \GLR{} test can only detect change-point on an arm that was played, and the \MCTopM{} orthogonalization procedure forces to play the same arm as long as the player is sitting.
}
